Considering scale in multilayer animal social networks

### 2020-06-29 paper/manuscript.Rmd
abstract edits

# Abstract
<!-- Scale remains a foundational concept in ecology. Social processes range from 
fine-scale interactions and co-occurrence to overlapping home ranges. Spatial 
scale has become a central consideration in the way we understand landscape ecology
and animal space use. Temporal variation in sociality and

Multilayer networks promise the explicit integration of social, 
spatial and temporal contexts of animal social networks.

-->

Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can range from fine-scale
interactions to co-occurrence and overlapping home ranges. Lastly,
sociality can vary within and across seasons. <!-- and vary within
and across seasons.--> Multilayer networks promise the explicit integration of
the social, spatial and temporal contexts. Given the complex interplay of
sociality and animal space use in heterogeneous landscapes, there remains an
important gap in our understanding of the influence of scale on animal social
networks. We discuss ways of considering social, spatial and temporal scale in
the context of multilayer caribou social networks. <!--We also present
perspectives on future development and applications of scale in multilayer
networks with respect to: phenotypes and individual fitness, movement ecology
and collective movement, and habitat selection and space use.--> Effective
integration of social and spatial processes, including biologically meaningful
scales, within the context of animal social networks is an emerging area of
research. We incorporate perspectives on how the social environment and spatial
processes are linked across scales in a multilayer context.

## Keywords
Social network analysis, Landscape ecology, Movement ecology, Space use

>>>>

# Abstract
Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, scale-dependent social processes can range from fine-scale
interactions to co-occurrence and overlapping home ranges. Furthermore,
sociality can vary within and across seasons. Multilayer networks promise the 
explicit integration of
the social, spatial and, temporal contexts. Given the complex interplay of
sociality and animal space use in heterogeneous landscapes, there remains an
important gap in our understanding of the influence of scale on animal social
networks. Using an empirical example, we discuss ways of considering social, spatial and, temporal scale in
the context of multilayer caribou social networks. Effective
integration of social and spatial processes, including biologically meaningful
scales, within the context of animal social networks is an emerging area of
research. We incorporate perspectives that link the social environment to spatial
processes across scales in a multilayer context.

## Keywords
Rangifer, Social network analysis, Habitat selection, Landscape ecology, Space use
